Responses to the Reviewers' Comments

### 2024-11-23 Response/Paper_Res.tex
Rev_V8.6
Rev_V9.2

@@

@@

Mobile edge computing (MEC) \cite{mao2017survey} has emerged as a promising technological solution to overcome the challenges faced by mobile devices (MDs) when performing high computational tasks, such as real-time data processing and artificial intelligence applications \cite{zhou2019edge} \cite{yousefpour2019all}. In spite of the MDs' technological advancements, their limited computing power and battery may lead to task drops, processing delays, and an overall poor user experience. By offloading intensive tasks to nearby edge nodes (ENs), MEC effectively empowers computation capability and reduces the delay and energy consumption. This improvement enhances the users' QoE, especially for time-sensitive computation tasks \cite{TNSE-QOE-24} \cite{ shah2018hierarchical}.

Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. Furthermore, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the computation offloading performance in MEC systems with limited resources.

%Researchers have recently proposed several task offloading algorithms to tackle the aforementioned issues. Mao \textit{et al.} in \cite{mao2016dynamic} introduced a computation offloading algorithm for MEC systems. This scheme aims to reduce the MD's energy consumption while meeting the computation delay constraints. In \cite{zhang2016energy}, Zhang \textit{et al.} proposed an offloading scheme for MEC in heterogeneous cellular networks, taking into account the energy-constrained MEC scenario and the heterogeneity of MDs when optimizing the offloading decisions. Bi \textit{et al.} in \cite{bi2018computation} proposed an algorithm to optimize decision-making about computation offloading and power transferring in a wireless-powered MEC. Ning \textit{et al.} in \cite{ning2018cooperative} introduced a heuristic algorithm designed to enhance the efficiency of the partial computation offloading model. The works in \cite{mao2016dynamic}-\cite{ning2018cooperative} primarily focus on quasi-static systems and are not well-suited for dynamic systems and time-varying conditions.

%The uncertain requirements and sensitive latency properties of computation tasks in MEC systems with limited resources pose nontrivial challenges that can significantly impact the computation offloading performance. In \cite{jovsilo2019wireless}, Josilo \textit{et al.} proposed a distributed algorithm based on a Stackelberg game. Lee \textit{et al.} in \cite{lee2019online} designed an algorithm based on online optimization techniques to minimize the maximum delay of the tasks in a hybrid edge-cloud network. Yang \textit{et al.} in \cite{yang2018distributed} explored an overhead minimization problem, aiming to jointly optimize delay and energy consumption in MEC. They proposed a distributed offloading algorithm to mitigate the wireless channel competition among MDs. The works \cite{jovsilo2019wireless}-\cite{yang2018distributed} considered delay-tolerant tasks, which may have a limited applicability due to the real-time processing demand of high computational tasks. Compared to these works, we explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which poses a more complex challenge.

%presents a more challenging problem. The impact of processing deadlines on the dynamic workload at the ENs influences the delay experienced by the offloaded tasks.

%In \cite{mao2016dynamic,zhang2016energy,bi2018computation,ning2018cooperative}, the processing capacity assigned to each MD by an EN remained unaffected by the number of offloaded tasks, resulting in a heavy load on the EN when a significant number of MDs offload their tasks to it. This heavy load can cause significant processing delays and even lead to missed deadlines and dropped tasks. To mitigate this issue, some existing works have proposed task offloading algorithms that consider the workloads at the ENs. In \cite{chen2018task}, Chen \textit{et al.} proposed an algorithm for task offloading in a software-defined ultra-dense network. The goal of this algorithm is to minimize task delay by formulating the task offloading scheme as a mixed integer non-linear program problem. Shah-Mansouri \textit{et al.} in \cite{shah2018hierarchical} proposed a QoE maximization slotwork for offloading decisions based on computation energy and delay reduction. They formulated a potential game to model competition among IoT users and achieved a close-to-optimal social cost.

%\subsection{Motivation and Contributions}

\textcolor{blue}{To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.}

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
\textcolor{blue}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into the D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust their offloading strategies to improve long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} \textcolor{blue}{ We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of MDs, this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs.}

	\item \textit{DRL-based Offloading Algorithm:} \textcolor{blue}{To solve the problem of long-term QoE maximization in highly dynamic mobile environments, we propose the QECO algorithm based on DRL, which empowers each MD to make offloading decisions independently, without prior knowledge of other MDs' tasks and offloading models. Focusing on the MD's QoE preference, our approach leverages D3QN and LSTM to prioritize and strike an appropriate balance between QoE factors while accounting for workload uncertainty at the ENs. QECO empowers MDs to anticipate the EN's load level over time, leading to more accurate offloading strategies. We also analyze the training convergence and computational complexity of the proposed algorithm.}

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanilla DQN and DDQN methods, while providing a substantial improvement of at least 34.8\% in average QoE. This advantage is achieved through prioritizing MD's QoE preferences, resulting in improvements of at least 12.2\%, 11.7\%, and 10.8\% in the average number of completed tasks, task delay, and energy consumption, respectively, when compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed}, the distributed and collective DRL-based offloading algorithm (DCDRL) \cite{qiu2020distributed}, and several benchmark methods.}

\textcolor{blue}{The structure of this paper is as follows. Section~\ref{section:II} reviews the related work. Section~\ref{section:III} presents the system model, followed by the problem formulation in Section ~\ref{section:IV}. In Section~\ref{section:V}, we present the algorithm, while Section~\ref{section:VI} provides an evaluation of its performance. Finally, we conclude in Section~\ref{section:VII}.}

	\section{Related Work}
	\label{section:II}
		In recent years, numerous studies have focused on computation offloading in MEC, covering a broad range of applications, including IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive}. 
		To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of DRL in adapting to environmental changes and learning optimal strategies. In this section, we explore the current DRL-based state-of-the-art works and discuss their strengths and limitations. Table~\ref{table1} provides an intuitive comparison of these works.
		\subsection{DRL-based Optimization Methods for MEC}

		There are two primary categories of related research in resource management for MEC based on target objectives, single-objective optimization and multi-objective optimization methods, where RL are mainstream optimization techniques.
		\subsubsection{Single-Objective Optimization} 
		Recent research has extensively explored single-objective optimization in the context of MEC, focusing on optimizing a single objective, such as delay or energy consumption. 
		Given the dynamic nature of MEC systems, in \cite{li2022integrated} the authors proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control. 
		Li \textit{et al.} in \cite{li2020joint} introduced a DRL-based delay-optimal offloading strategy that employs a DQN to learn offloading decisions autonomously. 
		To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
		Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
		To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
		Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
		Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility. 
		In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
		Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently.

		\subsubsection{Multi-Objective Optimization.}

		In MEC environments, multiple objectives often compete, requiring a balance in decision-making. For instance, task offloading must carefully navigate trade-offs between delay and energy consumption, as well as balance energy usage against the number of completed tasks. Research has increasingly addressed these multi-objective optimization challenges.
		Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
		To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DQN-based algorithm. 
		Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. 
		Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
		Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. 
		In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation.

		To further enhance the modeling of real-world scenarios, some studies have applied queuing theory to model MEC systems, which helps capture the dynamic nature of the network and allows MEC systems to allocate computational and transmission resources more efficiently.
		Liao \textit{et al.} in \cite{liao2023online} introduced a double DQN (DDQN)-based algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
		To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.
		Huang \textit{et al.} in \cite{huang2021deadline} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. 
		Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
		Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the IIoT systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
		To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.
		In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.

		\subsection{Analysis and Motivation}
		Despite extensive research efforts, task offloading continues to encounter significant challenges in real-world scenarios involving multiple MDs and ENs. We discuss these challenges from two aspects, i.e., system modeling and target objective optimization.

		\subsubsection{System modeling}

		Some existing works primarily focus on simplified MEC networks, investigating single MEC network models. For instance, studies \cite{zhou2021deep}, \cite{liu2021learn} only examine single-server or single-user scenarios, while \cite{huang2019deep}--\cite{wu2023computation} do not account for delay-sensitive tasks. In contrast, our research addresses a more realistic MEC scenario, considering delay-sensitive tasks with processing deadlines. This is challenging due to the interplay between processing deadlines, load dynamics at the ENs, and the resulting offloaded task delays. Additionally, the absence of robust underlying resource scheduling systems can lead to data congestion during transmission and inefficient resource allocation, hindering overall system performance \cite{wang2020reinforcement}--\cite{chen2021drl}. Hence, more accurate MEC models are necessary to handle the complexities of dynamic resource scheduling in large-scale scenarios.
		To better represent real-world scenarios, authors in \cite{Bolourian-WCL24}--\cite{9253665} have applied queuing theory to model MEC systems. This approach helps capture the dynamic nature of networks, enabling MEC systems to allocate computational and transmission resources more efficiently. In a similar vein, we approached the offloading process as a holistic queuing system, where multiple queues ensure fair resource scheduling for MEC, leading to more accurate and efficient resource management.

		In addition, the limited processing capacities of ENs necessitate careful consideration when allocating resources to MDs. The processing capacity allocated to an MD depends on the dynamic workload of an EN at any given time. Some studies have failed to account for these challenges in dynamic network environments, resulting in reduced system performance. For example, in \cite{chen2021drl}, it is assumed that MDs have sufficient transmission and computation resources from ENs, which may not reflect real-world conditions. While the works \cite{zhao2019deep}, \cite{dai2020edge}, and \cite{wu2024privacy} investigated limited resources in MEC, they did not consider dynamic workloads at ENs in decision-making processes, leading to potential performance issues.
		Certain studies such as \cite{sun2024hierarchical}, \cite{gong2022edge}-\cite{gao2022large} have addressed load levels at ENs and proposed task offloading algorithms. However, these algorithms often require global system information, resulting in high signaling overhead. In contrast to these works, we propose a distributed algorithm that effectively manages unknown load dynamics at ENs. This algorithm enables each MD to make offloading decisions independently, without requiring information (e.g., task models, offloading decisions) from other MDs, thereby reducing signaling overhead and improving overall system performance.

		\subsubsection{Optimization Objectives}
		Considering delay and energy consumption as optimization objectives represents a significant research focus in MEC. Most existing studies tend to optimize these two objectives independently, often neglecting the conflicts that arise between them, which can lead to skewed optimization results. Additionally, some research has prioritized maximizing the number of completed tasks, highlighting the advantages that MEC systems offer. Therefore, delay, energy consumption, and the number of completed tasks are critical factors in the design of MEC systems. However, to the best of our knowledge, there has been limited research that simultaneously addresses all three objectives.
		Different from works \cite{li2022integrated}-\cite{dai2020edge}, which only focus on delay-optimal optimization or energy-efficient optimization, we are motivated to emphasize the MEC system with delay, energy consumption, and the number of completed tasks as three objectives for QoE optimization. Multi-objective studies \cite{chen2021drl}-\cite{gao2022large} have mostly investigated the trade-off between two or three of these factors but fail to properly address user demands and fulfill QoE requirements. QoE is a time-varying performance measure that reflects user satisfaction, where each user may have unique QoE requirements according to the Mobile Devices' (MDs) individual preferences.
		In contrast to \cite{li2022integrated}-\cite{gao2022large}, to effectively address personalized QoE optimization, we define an adaptive trade-off between task completion and cost reduction. We introduce a weighted sum between completion delay and energy consumption as an associated cost. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes. \color{black}

>>>>

\usepackage{multirow}

@@

\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

edge computing (MEC) \cite{mao2017survey} has emerged as a promising technological solution to overcome the challenges faced by mobile devices (MDs) when performing high computational tasks, such as real-time data processing and artificial intelligence applications \cite{zhou2019edge} \cite{yousefpour2019all}. In spite of the MDs' technological advancements, their limited computing power and \textcolor{blue}{energy} may lead to task drops, processing delays, and an overall poor user experience. By offloading intensive tasks to nearby edge nodes (ENs), MEC effectively empowers computation capability and reduces the delay and energy consumption. This improvement enhances the users' quality of experience (QoE), especially for time-sensitive computation tasks \cite{TNSE-QOE-24} \cite{shah2018hierarchical}.

Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. \textcolor{blue}{In addition to the dynamic network changes, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the MEC systems.}

%In addition to the dynamic network changes, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the computation offloading performance in MEC systems with limited resources.

%To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives. While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.

To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives. \textcolor{blue}{However, the traditional RL methods are not efficient in handling environments with high-dimensional state  spaces. Deep reinforcement learning (DRL) combines  traditional RL  with  deep  neural  networks  to  intelligently respond to the unknown and dynamic system when addressing the limitations of RL-based algorithms. Despite these advancements, task offloading still faces significant challenges in real-world scenarios with multiple MDs and ENs. In such scenarios, it is essential for MDs to make offloading decisions independently  without prior knowledge of other MDs’ tasks and offloading models. However, existing works fail to adequately address this challenge. In addition, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, but also by energy consumption. Albeit some existing works have investigated the trade-off between delay and energy consumption, they fail to properly estimate the QoE value and address the users' requirements. Although deep Q-networks (DQN) offer a valuable tool, a more comprehensive approach is required to accurately estimate the QoE while addressing the aforementioned challenges in practical scenarios where global information is limited.}
%delay \cite{guo2022energy}
%energy consumption \cite{tang2022uav}
%trade-off between delay and energy consumption \cite{li2022joint}

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance.   \textcolor{blue}{We propose a distributed QoE-oriented computation offloading (QECO) algorithm to efficiently handle task offloading under uncertain loads at ENs.} This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
\textcolor{blue}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), which is a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into our D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust the offloading strategies to improve their long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} \textcolor{blue}{ We consider queuing systems for MDs and ENs and formulate the task offloading problem taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). We aim to maximize the long-term QoE, which reflects the task completion rate, task delay, and energy consumption of MDs. Our problem formulation effectively utilizes the resources and properly handles the dynamic fluctuations of workload at ENs. }
	%We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of MDs, this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs.

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate QECO’s performance and its training convergence against baseline schemes as well as two state-of-the-art existing works. The results demonstrate that our algorithm effectively utilizes the computing resources while taking the dynamic workloads at ENs into consideration. In particular, QECO converges more quickly than vanilla DQN and DDQN methods. QECO also improves average QoE by 37.1\% and 29.8\% compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

	%We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanilla DQN and DDQN methods while providing a substantial improvement by 37.1\%\,--\,29.8\% in average QoE compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and the distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.

	%This advantage is achieved through prioritizing MD's QoE preferences, resulting in improvements of at least 11.2\%, 11.7\%, and 8.3\% in the average number of completed tasks, task delay, and energy consumption, respectively

\end{itemize}
The structure of this paper is as follows.  \textcolor{blue}{Section~\ref{section:II} reviews the related works.} Section~\ref{section:III} presents the system model, followed by the problem formulation in Section ~\ref{section:IV}. In Section~\ref{section:V}, we present the algorithm, while Section~\ref{section:VI} provides an evaluation of its performance. Finally, we conclude in Section~\ref{section:VII}. \color{blue}

%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment. 
	%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
	%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
	%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}
	%, while uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges in MEC systems with limited resources. 
	% \textcolor{blue}{In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.}
	%To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.

	%\subsection{DRL-based Optimization Methods for MEC} 
	%\subsubsection{Single-Objective Optimization}

	%\textbf{Number of compeleted tasks optimization.}
	%\textbf{Delay-optimal algorithms.}  
	%\textbf{Energy-efficient algorithms.}

	%
	%\subsection{Single-Objective Optimization.} 
	%
	%\subsection{Delay and Energy Weighted-Objective Optimization.} 
	%
	%\subsection{Trade-off-Objectives Optimization.} 
	%

	%\subsubsection{Energy-efficient optimization.}

	%\subsubsection{Multi-Objective Optimization.}

	%In fact, the state of MD's computing and transmission power, arrived task's requirement, the energy state of MDs, and workloads at ENs all change dynamically with time in actual systems, 
	%On the other hand, although the works [11]–[15] considered non-divisible tasks, they do not take into account the underlying queuing systems. As a result, the processing and transmission of each task should always be accomplished within one time slot (or before the arrival of the next task), which may not always be guaranteed in practice.

	%In recent years, numerous studies have focused on computation offloading in MEC, covering a broad range of applications, including IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive}.

	%Recent research has extensively explored single-objective optimization in the context of MEC, focusing on optimizing a single objective, such as delay or energy consumption.

	%There are two primary categories of network performance optimization in MEC based on target objectives, single-objective optimization and conflicting multiple objective optimization approaches, where RL are mainstream optimization techniques.

	%Existing research on computation offloading in MEC systems can be roughly classified into two categories according to the optimization objectives, i.e., the delay-optimal computation offloading, the energy-optimal computation offloading, and the energydelay tradeoff computation offloading.

	% \subsection{Single-Objective Approachs}

	%Recent research has extensively explored single-objective optimization (SOO) in MEC, focusing on optimizing a single objective, such as delay or energy consumption.

	%\subsubsection{Time-sensetive approachs}

	%Li \textit{et al.} in \cite{li2020joint} introduced a DRL-based delay-optimal offloading strategy that employs a DQN to learn offloading decisions autonomously. 
	%\subsubsection{Energy-efficient approachs}

	%Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility.

	%\subsection{Conflicting Multiple-Objectives Optimization} 
	%In contrast to these SOO studies, recent efforts have focused on conflicting multiple-objective optimization (CMOO) in MEC,  where RL are mainstream optimization techniques. CMOO often involves conflicting objectives, requiring careful balancing in decision-making.

	%For example, task offloading must navigate trade-offs between delay and energy consumption, as well as balance energy usage with the number of completed tasks. 
	%\subsubsection{Delay-Energy Trade-off approaches}

	%%%To address time-sensitive applications with proccessing deadline, Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs.

	%To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.

	%\subsubsection{Delay, Energy, and Drop Balancing approaches}

	%%%Specifically, incorporating processing deadlines for time-sensitive applications in energy-constrained MEC systems adds significant complexity to the problem. This requires not only managing task delays and energy consumption but also maximizing the number of successfully completed tasks.
	%%%To further enhance the modeling of real-world scenarios, some studies have applied queuing theory to model MEC systems, which helps capture the dynamic nature of the network and allows MEC systems to allocate computational and transmission resources more efficiently.
	%%%%To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.

	%%%%Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration.

	%%%%To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.

	\color{blue}
	\section{Related Work}
	\label{section:II}

	To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. In this section, we explore the current RL-based state-of-the-art works and discuss their strengths and limitations. Table~\ref{table1} provides an intuitive comparison of these works.

	For time-sensitive applications, minimizing task delay is the primary optimization objective, driving the development of delay-optimal approaches in MEC. 
	To solve the delay minimization problem in MEC environment, Zhang \textit{et al.} in \cite{zhang2023offline} proposed an offline RL-based computation offloading algorithm, where the problem is modeled as a repeated game between two agents.
	Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources. Liu \textit{et al.} in \cite{liu2022deep} formulated the problem as MDP and proposed DRL-based approaches to minimize both communication and computation delay in MEC.
	To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
	Li \textit{et al.} in \cite{li2022integrated} proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control. 
	In \cite{wei2023many}, the authors investigated deadline-constrained time-sensitive tasks in vehicular MEC networks and proposed a multi-agent RL-based computation offloading algorithm based on POMDP to address joint delay and computation rate optimization. However, delay-optimal approaches~\cite{zhang2023offline}--\cite{wei2023many} often sacrifice other key performance metrics and may cause greater energy consumption or reduce the overall computation capacity, to achieve their~goal.

	%\cite{zheng2023drl} \cite{xue2023joint}
	For energy-constrained MEC systems, reducing energy consumption becomes a key objective, motivating the creation of energy-efficient approaches. 
	Munir \textit{et al.} \cite{munir2021multi}  investigated an energy dispatch problem of a self-powered wireless network with MEC capabilities and developed a semi-distributed approach using a multi-agent RL framework to minimize energy consumption.
	Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
	Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently. 
	%%In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
	To ensure that minimizing energy consumption does not lead to a reduction in the system's computing rate, researchers have expanded their work by incorporating the maximum tolerable delay for task models.
	In \cite{chouikhi2023energy}, Chouikhi \textit{et al.} proposed a computation offloading approach based on DRL to minimize long-term energy consumption and maximize the number of tasks completed before their tolerant deadlines.
	To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network. 
	Huang \textit{et al.} in \cite{huang2021deadline} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. 
	However, energy-efficient approaches~\cite{munir2021multi}--\cite{huang2021deadline}, even when considering deadline constraints, do not adequately address the complexities of time-sensitive applications, where reducing delay can have significant effects on the user's QoE. Particularly, saving transmission energy consumption may reduce the transmission power of MDs and lead to poor performance for real-time applications.
